---
title: "LLMs for Creativity"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    code_folding: hide
    fig_height: 5
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include = F}
library(tidyverse)
library(scales)
library(here)
library(knitr)
library(ggbeeswarm)
library(gridExtra)
library(ggalluvial)
library(patchwork)
library(reshape2)
library(lmerTest)
library(emmeans)
library(simr)
library(optimx)
```

# Set constants
```{r set-constants}
# set style
theme_set(theme_bw())

# set paths
figure_dir <- here("figures")
data_dir <- '/Users/harsh/Desktop/css-projs/creativity/analysis/'
```

# Load and clean data

```{r load-data}
hit_ids <- c("31YWE12TFJ2YJU9MF0GSJ7F9IRV7XE")

# read participants data
participants <- hit_ids %>%
  map_df(~read_csv(here(data_dir, sprintf("participants_%s.csv", .))))

# read responses
responses <- hit_ids %>%
  map_df(~read_csv(here(data_dir, sprintf("responses_%s.csv", .))))

```
## Remove anyone who looks spammy

Add exclusion criteria...

```{r filter}
# Filter participants based on 

```

# Design

This was a between-subjects design with 3 conditions...

Here are links to all three conditions:

* absent
* generate
* coach

# Sanity checks
## Randomization check

Check whether randomization is balanced across conditions (p-value should be large, indicating that the data are likely under the null of random assignment).

```{r check-random-assignment}
counts <- participants %>%
  count(condition)

kable(counts)

chisq.test(counts$n)

```
```{r diversity-by-condition}
# Calculate mean and standard error for each condition
diversity_summary <- participants %>%
  group_by(condition) %>%
  summarize(mean_diversity = mean(diversity),
            se = sd(diversity) / sqrt(n()))

# Plotting
ggplot(diversity_summary, aes(x = condition, y = mean_diversity)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_diversity - se, ymax = mean_diversity + se), width = 0.2) +
  labs(x = "Condition", y = "Diversity") +
  ggtitle("Diversity Across Conditions") +
  theme(legend.position = "none")
```


```{r perceived-difficulty-by-condition}
participants %>%
  mutate(difficulty = factor(`How difficult was it to come up with uses for the last object?`, levels = c("Very easy", "Somewhat easy", "Somewhat difficult", "Very difficult"))) %>%
  group_by(condition) %>%
  summarize(mean_difficulty = mean(as.numeric(difficulty)),
            se = sd(as.numeric(difficulty)) / sqrt(n())) %>%
  ggplot(aes(x = condition, y = mean_difficulty)) +
  geom_pointrange(aes(ymin = mean_difficulty - se, ymax = mean_difficulty + se)) +
  theme(legend.position = "none") +
  labs(x = 'Support Type', y = 'Perceived difficulty')
```


```{r originality-by-phase-by-condition}
# Group by phase, condition, and calculate mean and standard error of originality
originality_summary <- responses %>%
  group_by(phase, condition) %>%
  summarize(mean_originality = mean(originality),
            se = sd(originality) / sqrt(n()))

# Plotting with facets and no color aesthetic
ggplot(originality_summary, aes(x = phase, y = mean_originality)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_originality - se, ymax = mean_originality + se), width = 0.2) +
  geom_line(aes(group = condition)) +
  labs(x = "Phase", y = "Mean Originality") +
  ggtitle("Mean Originality Across Phases by Condition") +
  facet_wrap(~condition) +
  theme(legend.position = "none")
```


```{r originality-by-order-by-condition}
# Group by item_order, condition, and calculate mean and standard error of originality
originality_summary <- responses %>%
  group_by(item_order, condition) %>%
  summarize(mean_originality = mean(originality),
            se = sd(originality) / sqrt(n()))

# Plotting with facets and no color aesthetic
ggplot(originality_summary, aes(x = item_order, y = mean_originality)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_originality - se, ymax = mean_originality + se), width = 0.2) +
  geom_line(aes(group = condition)) +
  labs(x = "Item Order", y = "Mean Originality") +
  ggtitle("Mean Originality Across Item Orders by Condition") +
  facet_wrap(~condition) +
  theme(legend.position = "none")

#what was your strategy?
```


```{r fluency-by-condition-by-phase}
# Calculate the number of responses each worker has for each phase and condition
response_counts <- responses %>%
  group_by(worker_id, condition, phase) %>%
  summarize(num_responses = n()) %>%
  ungroup()

# Calculate the average number of responses for each phase and condition, along with standard error
response_summary <- response_counts %>%
  group_by(condition, phase) %>%
  summarize(mean_responses = mean(num_responses),
            se = sd(num_responses) / sqrt(n()))

# Plotting with facets
ggplot(response_summary, aes(x = phase, y = mean_responses)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_responses - se, ymax = mean_responses + se), width = 0.2) +
  geom_line(aes(group = condition)) +
  labs(x = "Phase", y = "Average Number of Responses") +
  ggtitle("Average Number of Responses per Worker Across Phases by Condition") +
  facet_wrap(~condition) +
  theme(legend.position = "none")
```


```{r fluency-by-condition-by-order}
# Calculate the number of responses each worker has for each item_order and condition
response_counts <- responses %>%
  group_by(worker_id, condition, item_order) %>%
  summarize(num_responses = n(), .groups = "drop")

# Calculate the average number of responses for each item_order and condition, along with standard error
response_summary <- response_counts %>%
  group_by(condition, item_order) %>%
  summarize(mean_responses = mean(num_responses),
            se = sd(num_responses) / sqrt(n()), .groups = "drop")

# Plotting with facets
ggplot(response_summary, aes(x = item_order, y = mean_responses)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_responses - se, ymax = mean_responses + se), width = 0.2) +
  geom_line(aes(group = condition)) +
  labs(x = "Item Order", y = "Average Number of Responses") +
  ggtitle("Average Number of Responses per Worker Across Item Orders by Condition") +
  facet_wrap(~condition) +
  theme(legend.position = "none")
```

# Primary hypotheses


